Looking at the India State Findings from the 1992 DHS Final Report

### 2022-03-31 outputs/paper/paper.Rmd
made markdown file for graphs

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Looking at the India State Findings from the 1992 DHS Final Report"
subtitle: ""
author: 
  - Bilal Haq
  - Ritvik Puri
thanks: "Code and data are available at: https://github.com/haqbilal/India-1992-DHS-State-Findings"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
